---
title: " SEC1- FA3 CUERDO,N.H.A-FA2"
author: "Cuerdo, Naomi Hannah A."
date: "2024-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# FA 2 

1. An experiment consists of tossing two fair coins. Use R to simulate this experiment 100 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting one head and one tail in any order.

## Initialization

```{r experiment}
num_exp <- 100

# Defining the outcomes
outcomes <- c("HH", "TT", "HT", "TH")

# Initializing the outcome counts
count_outcomes <- c(0, 0, 0, 0)
```

## performing the experiment

```{r calculations}
for (i in 1:num_exp) {
  coin1 <- sample(c("H", "T"), 1)
  coin2 <- sample(c("H", "T"), 1)
  
  outcome <- paste(coin1, coin2, sep = "")
  count_outcomes[outcomes == outcome] <- count_outcomes[outcomes == outcome] + 1
}

rel_freq <- count_outcomes / num_exp

# Check if "HT" and "TH" outcomes did not occur and set their relative frequency to 0 if so
if (sum(count_outcomes[outcomes %in% c("HT", "TH")]) == 0) {
  rel_freq[outcomes %in% c("HT", "TH")] <- 0
}
```

## printing the output
```{r}
# Print relative frequencies
for (i in 1:length(outcomes)) {
  cat("Relative frequency of outcome", outcomes[i], ":", rel_freq[i], "\n")
}
```

**relative frequency** refers to the proportion of times a particular outcome happens that is relative to the total number of trials or occurrences. These should sum up to 1 in decimal or 100% in perentages, as the represent all the possible outcomes of the events. 

```{r estimated probability}
# Calculate the probability of getting one head and one tail in no particular order
prob_onehead_onetail <- sum(rel_freq[outcomes %in% c("HT", "TH")])
print(paste("Estimated probability of getting one head and one tail in no particular order:", prob_onehead_onetail))

```
This result represents the probability of obtaining one head and one tail in any order when flipping two coins. 

## Figure 1
```{r bar graph}
#bar plot 
labels <- c("HH (Both Heads)", "TT (Both Tails)", "HT (Head, Tail)", "TH(Tail, Head)")
barplot(rel_freq, names.arg = labels, xlab = "Outcome", ylab = "Relative Frequency", col = "skyblue", main = "Relative Frequency of Outcomes in a Coin Flip")
        
```

Figure 1 shows the relative frequencies of different outcomes observed in the simulated coin flips. The x axis represents the different outcomes observed during the simulation, while the y-axis represents the relative frequency of each outcome.

Each bar on the graph corresponds to one of the outcomes and the height responds to the relative frequency of that outcome. From the graph, it is shown that both tails (TT) is more likely to happen in the simulation. 
